---
title: "CUNY Data 607 - Project 4- In Progress"
author: "Emilie M Bolduc"
date: "11/5/2017"
output: html_document
---

### Assignment
It can be useful to be able to classify new "test" documents using already classified "training" documents.  A common example is using a corpus of labeled spam and ham (non-spam) e-mails to predict whether or not a new document is spam.  

For this project, you can start with a spam/ham dataset, then predict the class of new documents (either withheld from the training dataset or from another source such as your own spam folder).  

### Solution
#### Libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(RCurl)
library(XML)
library(stringr)
library(tm)
```


#### Spam files
Take a look at the files
```{r}
length(list.files("spam_2"))
list.files("spam_2")[1:3]
```

Tried to rename spam files (this did not work)
```{r eval=FALSE}
file.rename(list.files(pattern="0*."), paste0("", 1:1396))
```

Look at the file format of one spam email
```{r}
file.info("spam_2/00001.317e78fa8ee2f54cd4890fdc09ba8176")
spam1 <- readLines("spam_2/00001.317e78fa8ee2f54cd4890fdc09ba8176")
spam1 <- str_c(spam1, collapse = "")
head(spam1)
```

#### Create Corpus for 1
```{r}
spam1_corpus <- Corpus(VectorSource(spam1))
spam1_corpus[[1]]
meta(spam1_corpus[[1]])
```

#### Combine all files into one big list
```{r}
file.list <- list.files("spam_2", pattern = "*.*")
head(file.list)
length(file.list)
setwd("/Users/emiliembolduc/Week 10 - Text Mining/Project 4/spam_2")
spam.list <- sapply(file.list, readLines)
class(spam.list)
```

#### Create corpus for all Spam
```{r}
SpamAll_corpus <- Corpus(VectorSource(spam.list)) %>%
  tm_map(content_transformer(tolower)) %>%
  tm_map(removeNumbers) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(removePunctuation) %>% 
  tm_map(stemDocument) %>% 
  tm_map(stripWhitespace) #%>%
SpamAll_corpus <- tm_map(SpamAll_corpus, removeNumbers)
```

#### Create a Term Document Matrix for all Spam
```{r}
Spam_tdm <- TermDocumentMatrix(SpamAll_corpus)
Spam_tdm
```

Wanted to check out what the data looks like...
```{r}
Spam_matrix <- as.matrix(Spam_tdm)
Spam_matrix <- sort(rowSums(Spam_matrix), decreasing = TRUE)
Spam_df <- data.frame(word = names(Spam_matrix),freq=Spam_matrix)
head(Spam_df, 50)
```


